Portfolio conservation of metapopulations under climate change\\Climate change and portfolio conservation of metapopulations\\Climate change and portfolio conservation\\Portfolio prioritization of salmon conservation\\Portfolio prioritization of metapopulation conservation

### 2013-06-12 inst/ms/ms.tex
Develop writing

In our ecological portfolios, we defined assets as stream-level
populations and the portfolios as salmon metapopulations (Table
\ref{t:port}). We use the terms \textit{stream} and \textit{populations}
interchangeably to represent the portfolio assets. We defined the
portfolio investors as the stakeholders in the fishery and
metapopulation performance. For example, we could consider fisheries
managers, conservation agencies, or First Nations groups as investors.
We defined asset value as the abundance of returning salmon in each
stream and value of the portfolio as the overall metapopulation
abundance. In this scenario, the equivalent to financial rate of return
is the generation-to-generation rate of change of metapopulation
abundance. We defined the financial asset investment weights as the
capacity of the stream populations --- specifically the unfinished
equilibrium stock size --- since maintaining or restoring habitat
requires money, time, and resources. Investment in a population
therefore represents investing in salmon habitat conservation or
reconstruction.

@@

Given strong short-term environmental fluctuations, conserving response
diversity buffers the risk properties of an ecological portfolio (Fig.
4a). In our simulation, the median variance of generation-to-generation
rate of change in abundance was X times lower given balanced response
diversity (full range of responses or most stable only vs.~conserving
one half or the other). In fact, even though by conserving the full
range of responses, the portfolio was comprised of warm and
cool-thriving populations that were more variable on their own, each was
balanced by an opposing population. The portfolio risk was therefore
comparable between the full range of responses and most stable only
portfolios.

We can see the mechanism behind these portfolio properties by inspecting
example population time series (Fig. 4c, d). If only the upper or lower
half of response diversity is conserved, the portfolio tends to do well
or poorly depending on the environmental conditions (Fig. 4d). This risk
is buffered with balanced response diversity (Fig. 4c).

@@

Given long-term environmental change, the choice of which populations to
conserve affects the return properties of an ecological portfolio (Fig.
4b). By conserving balance response diversity, an ecological manager is
hedging his or her bets on what will happen with the environment and how
the populations will respond. The typical return for a balanced response
diversity strategy was zero --- the metapopulation neither increased or
decreased in abundance in the long run. By conserving only the upper or
lower half of response diversity, a conservation manager is putting all
his or her eggs in one basket --- the metapopulation might do really
well through time or it might do really poorly. The example
metapopulation abundance time series (Fig. 4d, f) illustrate this
effect. By conserving response diversity, when one population is doing
poorly, another is doing well and the metapopulation abundance remains
stationary through time.

Notably, in theses simulations, if a managers invested in the
populations that were doing well at the beginning they would have had
the lowest rate-of-return portfolio in the end (purple portfolios in
Fig. 4b).

@@

Given a scenario where we don't know the distribution of
population-level response diversity, portfolio optimization informs us
about the risk buffering from maintaining multiple populations (Fig. 5).
In short, investing in more populations buffers portfolio risk.

@@

Given short-term environmental noise, conserving more populations
buffers portfolio risk while the random conservation of response
diversity creates a spread of metapopulation risk for the same number of
populations conserved (Fig. 5a). For example, a metapopulation with
eight conserved populations is X times less risky than a metapopulation
with only four. We can see this risk-buffering effect through example
metapopulations in Fig. 5c and 5d. We note that the risk-return axes of
portfolio optimization ignore the absolute-abundance dimension (Fig.
5d). As one would expect, conserving fewer populations also results in
lower-abundance metapopulations.

@@

Given long-term environmental noise, conserving more populations also
buffers portfolio risk. However, in contrast to the short-term
environmental noise scenario, the unknown response diversity creates a
spread of possible metapopulation return for the same number of
conserved populations (Fig. 5b). Here, the number of populations
conserved buffers non-systematic (i.e.~not-environmentally-driven)
stochasticity.

>>>>

In our ecological portfolios, we defined assets as stream-level populations and the portfolios as salmon metapopulations (Table \ref{t:port}). We use the terms \emph{stream} and \emph{populations} interchangeably to represent the portfolio assets. We defined the portfolio investors as the stakeholders in the fishery and metapopulation performance. For example, we could consider fisheries managers, conservation agencies, or First Nations groups as investors. We defined asset value as the abundance of returning salmon in each stream and value of the portfolio as the overall metapopulation abundance. In this scenario, the equivalent to financial rate of return is the generation-to-generation rate of change of metapopulation abundance. We defined the financial asset investment weights as the capacity of the stream populations --- specifically the unfinished equilibrium stock size --- since maintaining or restoring habitat requires money, time, and resources. Investment in a population therefore represents investing in salmon habitat conservation or reconstruction.

@@

Given strong short-term environmental fluctuations, conserving response diversity buffers the risk properties of an ecological portfolio (Fig.~\ref{f:sp-mv}a). In our simulation, the median variance of generation-to-generation rate of change in abundance was X times lower given balanced response diversity (full range of responses or most stable only vs.~conserving one half or the other). In fact, even though by conserving the full range of responses, the portfolio was comprised of warm and cool-thriving populations that were more variable on their own, each was balanced by an opposing population. The portfolio risk was therefore comparable between the full range of responses and most stable only portfolios.

We can see the mechanism behind these portfolio properties by inspecting example population time series (Fig.~\ref{f:sp-mv}c, d). If only the upper or lower half of response diversity is conserved, the portfolio tends to do well or poorly depending on the environmental conditions (Fig.~\ref{f:sp-mv}d). This risk is buffered with balanced response diversity (Fig.~\ref{f:sp-mv}c).

@@

Given long-term environmental change, the choice of which populations to conserve affects the return properties of an ecological portfolio (Fig.~\ref{f:sp-mv}b). By conserving balance response diversity, an ecological manager is hedging his or her bets on what will happen with the environment and how the populations will respond. The typical return for a balanced response diversity strategy was zero --- the metapopulation neither increased or decreased in abundance in the long run. By conserving only the upper or lower half of response diversity, a conservation manager is putting all his or her eggs in one basket --- the metapopulation might do really well through time or it might do really poorly. The example metapopulation abundance time series (Fig.~\ref{f:sp-mv}d, f) illustrate this effect. By conserving response diversity, when one population is doing poorly, another is doing well and the metapopulation abundance remains stationary through time.

Notably, in theses simulations, if a managers invested in the populations that were doing well at the beginning they would have had the lowest rate-of-return portfolio in the end (purple portfolios in Fig.~\ref{f:sp-mv}b).

@@

Given a scenario where we don't know the distribution of population-level response diversity, portfolio optimization informs us about the risk buffering from maintaining multiple populations (Fig.~\ref{f:n-mv}). In short, investing in more populations buffers portfolio risk.

@@

Given short-term environmental noise, conserving more populations buffers portfolio risk while the random conservation of response diversity creates a spread of metapopulation risk for the same number of populations conserved (Fig.~\ref{f:n-mv}a). For example, a metapopulation with eight conserved populations is X times less risky than a metapopulation with only four. We can see this risk-buffering effect through example metapopulations in Fig.~\ref{f:n-mv}c and \ref{f:n-mv}d. We note that the risk-return axes of portfolio optimization ignore the absolute-abundance dimension (Fig.~\ref{f:n-mv}d). As one would expect, conserving fewer populations also results in lower-abundance metapopulations.

@@

Given long-term environmental noise, conserving more populations also buffers portfolio risk. However, in contrast to the short-term environmental noise scenario, the unknown response diversity creates a spread of possible metapopulation return for the same number of conserved populations (Fig.~\ref{f:n-mv}b). Here, the number of populations conserved buffers non-systematic (i.e.~not-environmentally-driven) stochasticity.
